Reproducibility and Open Science in Economics

### 2025-07-17 article.tex
Should be pretty complete

In order to write about ``Open Science,'' a definition is needed. Open science is a surprisingly difficult term to define precisely. 
%
\citet{unesco_understanding_2022} sees four components to open \textbf{science}: \textit{open   scientific   knowledge }(publications, data, code, and teaching materials ``openly    available, accessible and reusable for everyone''),     open     science     \textit{infrastructures} (which encompasses both physical infrastructure such as instruments and laboratories, as well as virtual components such as open access publication platforms),     science     \textit{communication} (knowledge translation),  and broad \textit{engagement} beyond the boundaries of the academy. It also recognizes the limitations of such access in a caveat:

@@

One way to start to move away from a binary perspective of access is to consider \textbf{time} as summary metric that captures what is needed in order to access generic resources, whether data, manuscripts, or computing resources. Time might be needed to write an application to access data, or time might be needed in order to obtain access to large-scale computing resources. Time might be needed in order to obtain grant funding that allows to purchase such resources. I choose time, rather than money, as the metric, since it might appear to be slightly more egalitarian, given that much of science has (theoretical) access to subsidies and grants. In the other dimension,  the number of people who have some probability of accessing the resource (the \textbf{size of the network}) can be taken as an approximate measure of openness. Figure~\ref{fig:nxt}, taken from \citet{vilhuber_reproducibility_2023}, serves to illustrate this idea, for access to data, with various institutions that facilitate that access mapped out into the space of time vs. size of network. I will return to this throughout the discussion.

@@

\paragraph{Organic data:} However, most economists, when asked about data subject to restrictions, will think of ``proprietary data,'' a term often applied to any data that may be subject to restrictions of use and re-use. Access to most administrative data is typically not ``open'' in the sense of OKF, but are they open enough, given the privacy concerns that are attached to these data? Many have argued that access is not broad enough \citep{card_expanding_2010,einav_economics_2014}, while acknowledging the difficulty of addressing privacy and security of the data at scale. \citet{abowd_economic_2018} discuss the challenge of making the choice of between accuracy of (public) statistics and data, and the privacy loss inherent in doing so. \citet{nagaraj_improving_2020} argue that more openness improves scientific progress, and \citet{nagaraj_how_2023} study this in the context of the US system for providing access (\ac{FSRDC}). They note that 4\% of US-based empirical authors have had some access to the FSRDC system. I am not aware of similar studies for other countries, such as France \citep[the equivalent system is the \ac{CASD}, ][]{gadouche_centre_2019} or Canada \citep{currie2015social}. In absolute terms, these networks host several hundred researchers every year. For the 781 projects using Census Bureau data in the \ac{FSRDC}, 2,084 researchers  have had access to confidential data between 1998 and 2024.\footnote{Own calculations based on Census Bureau data, see \url{https://labordynamicsinstitute.github.io/fsrdc-external-census-projects/}.} \citet{nagaraj_how_2023} mention 861 papers in scientific journals. Similar numbers can be obtained for the French (6841 researchers from 1109 institutions on 1797 projects with 417 publications)\footnote{From \url{https://www.casd.eu/} and \url{https://www.casd.eu/toutes-les-publications/liste/0/20/} as of May 2025.}
% https://www.casd.eu/toutes-les-publications/liste/0/20/ 
% 20 pages à 20 publications et 1 à 17 = 417
and Canadian (2201 active researchers from 42 universities as of January 2025, with 3245 papers published between 2000 and May 2024)\footnote{Provided by Grant Gibson, CRDCN, on February 10, 2025.} networks.\footnote{The \citet{nagaraj_how_2023} number only includes papers published by economists. Other numbers are counts of researchers and publications in all disciplines, in non-peer-reviewed publications, and include non-economists.} The number of publications from access to these networks is smaller in absolute terms then those from PSID and SOEP, though likely higher in impact \citep{nagaraj_how_2023}.

@@

An informal survey of several economists working with colleagues and students in Latin America, Africa, and Asia uniformly suggested that access to commercial statistical software was often difficult for students, alleviated somewhat when students were fortunate to attend private universities. In fact, in a recent survey conducted by CIDR,\marginpar{Needs citation} respondents were asked to name the top two factors that could support early-career African scholars’ publication success. 
% new version
55\% of African scholars noted that providing access to research resources, such as journals, datasets, and software would improve their journal acceptance rate.%
%
% Previously:
%46\% of respondents chose 
%`Providing access to datasets and data management tools' as one of the two factors. University staff and students (across multiple disciplines) were also asked which aspect they  most needed funding for, and 38\% mentioned `Data analysis software' \citep{sheth_understanding_nodate}. 
Within top universities, on the other hand, most researchers, including graduate students, will have access to these software products, and even many undergraduates may be able to leverage university computer labs to access these software. At lower-ranking institutions and outside of academia, however, it may be more constraining, even in Europe or the United States. Precise information is hard to come by.\footnote{To a smaller degree, the problem also arises for \textbf{compilers}. While there are open-source compilers for Fortran and C (GNU Fortran, LLVM Flang), many economists will use what they consider to be more efficient commercial compilers, which may require the payment of  subscription fees (e.g., Intel, NAG Fortran, PGI (now Nvidia)). More recently, some of the commercial compilers (Intel, Nvidia) have become freely available. Some numerical (non-linear) optimizers (e.g., Gurobi, Knitro) may also require payment of fees, though some limited academic free use may be available.}
%
% In the Central African Republic, one month of internet access costs more than 1.5 times the annual per capita income. \citep[World Development Report 2016, via ][]{schia2018} More broadly, 
% Aside from a broader concern about accessibility of information technology in less developed countries (see f.i. World Development Report 2016), the availability in particular in the education sector is key to improving skills of future workers. However, as the 2016 report points out, `` there is an alarming lack of accurate and timely data on ICT use in the developing world.'' (WD 2016, pg. 219)

@@

Most often, the discussion about benefits of open science center around \textit{data} availability. The World Bank, in its annual World Development Report, identifies data availability --- for research, for commerce, for education --- as a key contributor, and highlights that many LMIC continue to have impediments to the reliable provision of open access data \citep[, pg. 62]{world_bank_world_2021}. The (theoretical) optimal level of data availability intersects with privacy, making the optimal level of data availability a non-trivial balance between public and private benefits, and private costs \citep{duch-brown_economics_2017,acquisti_economics_2016,abowd_suboptimal_2019,abowd_economic_2018}. The more recent discussions (and court cases) surrounding the use of data in the training of large language models have only re-emphasized this tension \citep{panettieri_generative_2025}.

A different thread in the discussion brings up normative reasons for transparency, for instance around Mertonian \citep{merton1942note} norms of openness

The  benefits of open science have often been measured indirectly, through increased citations, say. Some recent studies find some advantages for studies with linked (openly available) data \citep{piwowar_data_2013,colavizza_citation_2020,christensen_study_2019}.\footnote{Some of these studies need to be taken with a grain of salt, since they typically measure whether data is referenced, not whether it is actually openly available.} The economics literature has emphasized the benefits of (balanced) open science. \citet{nagaraj_improving_2020} discuss the canonical example of improved data access through (free) public-use data in the context of satellite imagery. Patents can be usefully investigated, since they are both openly viewable but also access-limiting by their very nature. Economists have looked at how restrictiveness, duration, and type of patents affect scientific progress. In general, restrictions reduce social welfare \citep{williams_intellectual_2013,murray_mice_2016}, even enabling anti-competitive behavior that directly identify welfare loss \citep{xie_anticompetitive_2020}. The much broader applicability of open science practices is also much more recent, and as of yet, hard to measure. Nevertheless, it appears to be widely accepted in economics, as evidenced by very strong positive attitudes (

@@

    &  
    \includegraphics[width=0.65\linewidth]{data/christensen-2019-fig7.png}
    \\
    \includegraphics[width=0.25\linewidth]{data/christensen-2019-fig1-legend.png}
         &  
    \includegraphics[width=0.5\linewidth]{data/christensen-2019-fig7-legend.png}
    \\
    \end{tabular}
    \caption{Extracts from \citet[Figures 1 and 7]{ferguson_survey_2023}, reused under CC-BY 4.0.}
    \label{fig:christensen-fig1b}
\end{figure}

@@

\subsection{Two concrete examples in economics}

To illustrate some of the benefits of open science in economics, I describe two recent articles in economics that leverage the availability of code and data to improve econometric methods for future researchers. The first paper relies on the empirical recomputation of prior papers to assess a theoretically ambiguous potential bias in inference. The second paper also focuses on inference, and uses actual data from previous papers to simulate the relevance of the impact. Both then provide new software (R and Stata packages), under open source licenses, to ``fix'' the problem for future studies.

\citet{roth_pretest_2022}  uses 12 previously published papers to assess whether the usual tests for pre-existing differences in trends when using difference-in-differences methods are properly controlling for power, and the empirical impact on subsequent inference. The theoretical bias is ambiguous, so an empirical evaluation is necessary. The study both leverages the open availability of materials in economic journals, but also illustrates the limitations imposed by imperfect adherence to openness. To wit, Roth writes that he searched for

\begin{quote}
``the phrase “event study” in papers published in the \textit{American Economic Review, American Economic Journal: Applied Economics}, and \textit{American Economic Journal: Economic Policy} between
2014 and June 2018 ... The search returned 70 total papers that include a figure that the authors describe as an event-study plot.''
\end{quote}

but continues to then be limited by lack of data in the majority of cases:

@@

In both of these examples, the ability to access prior data, code, and information is critical to improving future scientific progress, but is limited by both historical and unavoidable limitations on openness.

% also Goldsmith-Pinkham, Paul, Hull, Peter, and Kolesar, Michal. Data and Code for: Contamination Bias in Linear Regressions. Nashville, TN: American Economic Association [publisher], 2025. Ann Arbor, MI: Inter-university Consortium for Political and Social Research [distributor], 2025-01-03. https://doi.org/10.3886/E207983V1
%
\begin{quote}
    ``These studies were identified by a systematic search of papers in the AEA Data and Code Repository''
\end{quote}

@@

At the time of this writing, I have three editorial appointments. I am the Data Editor for the journals of the \acf{AEA}, the joint executive editor for the open access and multi-disciplinary \ac{JPC}, and I am a column editor for the open access \ac{HDSR}. I will use each of these to highlight a particular pattern in broadening access to publications, without any claim to generality.

@@

>>>>

In order to write about ``Open Science,'' a definition is needed. Open science is a surprisingly difficult term to define precisely, and multiple overlapping definition are commonly referenced. 
%
\citet{unesco_understanding_2022} sees four components to open \textbf{science}: \textit{open   scientific   knowledge }(publications, data, code, and teaching materials ``openly    available, accessible and reusable for everyone''),     open     science     \textit{infrastructures} (which encompasses both physical infrastructure such as instruments and laboratories, as well as virtual components such as open access publication platforms),     science     \textit{communication} (knowledge translation),  and broad \textit{engagement} beyond the boundaries of the academy. It also recognizes the limitations of such access in a caveat:

@@

One way to start to move away from a binary perspective of access is to consider \textbf{time} as summary metric that captures what is needed in order to access generic resources, whether data, manuscripts, or computing resources. Time might be needed to write an application to access data, or time might be needed in order to obtain access to large-scale computing resources. Time might be needed in order to obtain grant funding that allows to purchase such resources. I choose time, rather than money, as the metric, since it might appear to be slightly more egalitarian, given that much of science has (theoretical) access to subsidies and grants. In the other dimension,  the number of people who have some probability of accessing the resource (the \textbf{size of the network}) can be taken as an approximate measure of openness, regardless of how interesting or valuable they might consider the data to be. Figure~\ref{fig:nxt}, taken from \citet{vilhuber_reproducibility_2023}, serves to illustrate this idea, for access to data, with various institutions that facilitate that access mapped out into the space of time vs. size of network. I will return to this throughout the discussion.

@@

\paragraph{Organic data:} However, most economists, when asked about data subject to restrictions, will think of ``proprietary data,'' a term often applied to any data that may be subject to restrictions of use and re-use. Access to most administrative data is typically not ``open'' in the sense of OKF, but are they open enough, given the privacy concerns that are attached to these data? Many have argued that access is not broad enough \citep{card_expanding_2010,einav_economics_2014}, while acknowledging the difficulty of addressing privacy and security of the data at scale. \citet{abowd_economic_2018} discuss the challenge of making the choice of between accuracy of (public) statistics and data, and the privacy loss inherent in doing so. \citet{nagaraj_improving_2020} argue that more openness improves scientific progress, and \citet{nagaraj_how_2023} study this in the context of the US system for providing access (\ac{FSRDC}). They note that 4\% of US-based empirical authors have had some access to the FSRDC system. I am not aware of similar studies for other countries, such as France \citep[the equivalent system is the \ac{CASD}, ][]{gadouche_centre_2019} or Canada \citep{currie2015social}. In absolute terms, these networks host several hundred researchers every year. For the 781 projects using Census Bureau data in the \ac{FSRDC}, 2,084 researchers  have had access to confidential data between 1998 and 2024.\footnote{Own calculations based on Census Bureau data, see \url{https://labordynamicsinstitute.github.io/fsrdc-external-census-projects/}.} \citet{nagaraj_how_2023} mention 861 papers in scientific journals. Similar numbers can be obtained for the French (6841 researchers from 1109 institutions on 1797 projects with 417 publications)\footnote{From \url{https://www.casd.eu/} and \url{https://www.casd.eu/toutes-les-publications/liste/0/20/} as of May 2025.}
% https://www.casd.eu/toutes-les-publications/liste/0/20/ 
% 20 pages à 20 publications et 1 à 17 = 417
and Canadian (2201 active researchers from 42 universities as of January 2025, with 3245 papers published between 2000 and May 2024)\footnote{Provided by Grant Gibson, CRDCN, on February 10, 2025.} networks.\footnote{The \citet{nagaraj_how_2023} number only includes papers published by economists. Other numbers are counts of researchers and publications in all disciplines, in non-peer-reviewed publications, and include non-economists.} The number of publications from access to these networks is smaller in absolute terms then those from PSID and SOEP, though likely higher in impact \citep{nagaraj_how_2023}.\footnote{For an analysis of code availability over time for SOEP-based publications, see \citet{fink_replication_2025}.}

@@

An informal survey of several economists working with colleagues and students in Latin America, Africa, and Asia uniformly suggested that access to commercial statistical software was often difficult for students, alleviated somewhat when students were fortunate to attend private universities. In fact, in a recent survey conducted by CIDR \citep{shipow-cidr}, respondents were asked to name the top two factors that could support early-career African scholars’ publication success. 
% new version
55\% of African scholars noted that providing access to research resources, such as journals, datasets, and software would improve their journal acceptance rate.%
%
% Previously:
%46\% of respondents chose 
%`Providing access to datasets and data management tools' as one of the two factors. University staff and students (across multiple disciplines) were also asked which aspect they  most needed funding for, and 38\% mentioned `Data analysis software' \citep{sheth_understanding_nodate}. 
Within top universities, on the other hand, most researchers, including graduate students, will have access to these software products, and even many undergraduates may be able to leverage university computer labs to access these software. At lower-ranking institutions and outside of academia, however, it may be more constraining, even in Europe or the United States. Precise information is hard to come by, but  Figure~\ref{fig:downloads} provides some insights whether this might, in fact, hold. The data plotted relates, by various regions, the relative importance of that region in global Stata and R downloads.\footnote{See Appendix for a detailed explanation of several important caveats.}. The top panel summarizes this by ``Global North'' and ``South,'' and the juxtaposition would suggest that the countries of the Global South are heavier users of the free R software, rather than the paid-for Stata software. However, the bottom panel moderates that view somewhat when breaking this out by continents. It turns out that the richest continent (North America) is the heaviest R user, and that Africa is a heavier user of Stata. Thus, there is, at best, very weak evidence that the cost of software matters, in the aggregate.

\input{figure4}

\footnote{To a smaller degree, the problem also arises for \textbf{compilers}. While there are open-source compilers for Fortran and C (GNU Fortran, LLVM Flang), many economists will use what they consider to be more efficient commercial compilers, which may require the payment of  subscription fees (e.g., Intel, NAG Fortran, PGI (now Nvidia)). More recently, some of the commercial compilers (Intel, Nvidia) have become freely available. Some numerical (non-linear) optimizers (e.g., Gurobi, Knitro) may also require payment of fees, though some limited academic free use may be available.}
%
% In the Central African Republic, one month of internet access costs more than 1.5 times the annual per capita income. \citep[World Development Report 2016, via ][]{schia2018} More broadly, 
% Aside from a broader concern about accessibility of information technology in less developed countries (see f.i. World Development Report 2016), the availability in particular in the education sector is key to improving skills of future workers. However, as the 2016 report points out, `` there is an alarming lack of accurate and timely data on ICT use in the developing world.'' (WD 2016, pg. 219)

@@

Tthe discussion about benefits of open science often centers around \textit{data} availability. The World Bank, in its annual World Development Report, identifies data availability --- for research, for commerce, for education --- as a key contributor, and highlights that many LMIC continue to have impediments to the reliable provision of open access data \citep[, pg. 62]{world_bank_world_2021}. The (theoretical) optimal level of data availability intersects with privacy, making the optimal level of data availability a non-trivial balance between public and private benefits, and private costs \citep{duch-brown_economics_2017,acquisti_economics_2016,abowd_suboptimal_2019,abowd_economic_2018}. The more recent discussions (and court cases) surrounding the use of data in the training of large language models have only re-emphasized this tension \citep{panettieri_generative_2025}.

A different thread in the discussion brings up normative reasons for transparency, for instance around Mertonian \citep{merton1942note} norms of openness \citep[see ][for an overview]{miguel_evidence_2021}. Openness at all stages of research may act as a moderator for publication bias \citep{miguel_evidence_2021,brodeur_star_2016}

Some of the  benefits of open science have  been measured indirectly, through increased citations, say. Some recent studies find some advantages for studies with linked (openly available) data \citep{piwowar_data_2013,colavizza_citation_2020,christensen_study_2019}.\footnote{Some of these studies need to be taken with a grain of salt, since they typically measure whether data is referenced, not whether it is actually openly available.} The economics literature has emphasized the benefits of (balanced) open science. \citet{nagaraj_improving_2020} discuss the canonical example of improved data access through (free) public-use data in the context of satellite imagery. Patents can be usefully investigated, since they are both openly viewable but also access-limiting by their very nature. Economists have looked at how restrictiveness, duration, and type of patents affect scientific progress. In general, restrictions reduce social welfare \citep{williams_intellectual_2013,murray_mice_2016}, even enabling anti-competitive behavior that directly identify welfare loss \citep{xie_anticompetitive_2020}. The much broader applicability of open science practices is also much more recent, and as of yet, hard to measure. Nevertheless, it appears to be widely accepted in economics, as evidenced by very strong positive attitudes documented in \citet{ferguson_survey_2023}, as selectively depicted in  Figure~\ref{fig:christensen-fig1b}. The top left part of Figure~\ref{fig:christensen-fig1b} shows behavior (black) and opinions (color scale) in regards to data sharing among economists, with more than 50\% of economists having shared data, but over 90\% being very much or moderately (the two green colors) in favor of sharing data. The right panel illustrates the evolution over time, depicting the proportion of social scientists in the four disciplines (economics, political science, psychology, and sociology) who had adopted an open science practice as of a particular date, showing again the rapid increase in active data sharing amongst economists from around 60\% in 2011 to the 2020 number of over 90\%.

@@

    &  
    \includegraphics[width=0.65\linewidth]{data/christensen-2019-fig7.png}
    \\
    \includegraphics[width=0.30\linewidth]{data/christensen-2019-fig1-legend.png}
         &  
    \includegraphics[width=0.5\linewidth]{data/christensen-2019-fig7-legend.png}
    \\
    \end{tabular}
    \caption{Extracts from \citet[Figures 1 and 7]{ferguson_survey_2023}, reused under CC-BY 4.0.}
    \label{fig:christensen-fig1b}
\end{figure}

@@

I want to add to this discussion of benefits three concrete case studies that advance science in economics, while relying heavily on the openness of prior research. The three articles in question  leverage the open availability of code and data, with licenses that allow for re-use, to improve econometric methods for future researchers. The first paper relies on the empirical recomputation of prior papers to assess a theoretically ambiguous potential bias in inference. The second paper also focuses on inference, and uses actual data from previous papers to simulate the relevance of the impact. Both then provide new software (R and Stata packages), under open source licenses, to ``fix'' the problem for future studies. The third study selects studies again where data are available, and leverages the centralized availability of such replication packages to select the studies in their sample.

\citet{roth_pretest_2022}  uses 12 previously published papers to assess whether the usual tests for pre-existing differences in trends when using difference-in-differences methods are properly controlling for power, and the empirical impact on subsequent inference. The theoretical bias is ambiguous, so an empirical evaluation is necessary. The study both leverages the open availability of materials in economic journals, but also illustrates the limitations imposed by imperfect adherence to openness. To wit, Roth writes that he searched for 
%
\begin{quote}
``the phrase “event study” in papers published in the \textit{American Economic Review, American Economic Journal: Applied Economics}, and \textit{American Economic Journal: Economic Policy} between
2014 and June 2018 ... The search returned 70 total papers that include a figure that the authors describe as an event-study plot.''
\end{quote}
%
but continues to then be limited by lack of data in the majority of cases:

@@

Finally, \citet{goldsmith-pinkham_contamination_2024} investigate contamination bias (``each treatment’s effect are contaminated by nonconvex averages of the effects of other treatments''). To do so, they search the centralized repository of AEA replication packages\footnote{``These studies were identified by a systematic search of papers in the AEA Data and Code Repository.'' [pg. 4043]} to identify  packages that, crucially, contain data. They then reproduce one of each original paper's specifications, conduct several tests, and conclude that ``economically and statistically meaningful contamination bias [is present] in two of the three observational studies while showing no evidence for bias in any of the experimental studies.'' (pg. 4046). \citet{goldsmith-pinkham_contamination_2024}  has been cited between 65 and 118 (OA, GS) times.\footnote{Google Scholar citations are directly reported from a view of the article's page on Google Scholar, and may include citations to multiple versions. OpenAlex citations are the sum of citations to all recorded works on OA with the same title and by the same authors.}

In each of these examples, the ability to access prior data, code, and information is critical to improving future scientific progress. In some cases, it remains limited by both historical and unavoidable limitations on openness, as well as scaling limitation based on absence of ``push button'' reproducibility.

% also Goldsmith-Pinkham, Paul, Hull, Peter, and Kolesar, Michal. Data and Code for: Contamination Bias in Linear Regressions. Nashville, TN: American Economic Association [publisher], 2025. Ann Arbor, MI: Inter-university Consortium for Political and Social Research [distributor], 2025-01-03. https://doi.org/10.3886/E207983V1
%

@@

Over the past eight years, I have or have had three editorial appointments. I am the Data Editor for the journals of the \acf{AEA} \citep{10.1257/pandp.108.745},  a column editor for the open access \ac{HDSR} \citep{vilhuberReinforcingReproducibilityReplicability2023}, and until January 2025, the joint executive editor for the open access and multi-disciplinary \ac{JPC}, for which I continue to manage the publication infrastructure \citep{abowd_changes_2025}. I will use each of these to highlight a particular pattern in broadening access to publications, without any claim to generality.

@@

\subsection*{Inferring Stata and R usage}

Stata usage is inferred from downloads of Stata packages from the SSC web server, which is the sole official location to obtain these packages. Private mirrors may exist, and not all Stata packages are installed from SSC - both the Stata Journal and Github are likely to be significant sources. Data are obtained from log files from the SSC web server, provided by Kit Baum. R usage is inferred from downloads of  R binaries (for Windows and MacOS). While this is likely to be less frequent than Stata packages, relative patterns are of interest. There is no easy way to obtain the full list of downloads for all packages, other than cycling through several thousand such packages. The data stem from one of dozens of \ac{CRAN} mirrors, though this one, managed by Posit PBC, is the first one listed in the list of mirrors that are offered to users. Data in both cases is for February 2025.

As a first step, these downloads were mapped to countries, and then aggregated by regions (Table~\ref{tab:stata_downloads_regional_stats_2024} for Stata, Table~\ref{tab:r_downloads_regional_stats_2024} for R).
%
%
\input{outputs/stata_downloads_regional_stats_select}
\input{outputs/r_downloads_regional_stats_select}
%
Mapped onto a world map, this provides a pretty picture, though not very informative (Figure~\ref{fig:stata_r_world}).
\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{outputs/stata_downloads_world_map_2024_nochina.png}

    \includegraphics[width=0.8\textwidth]{outputs/r_downloads_world_map_2024_nochina.png}
    \caption{Downloads of Stata packages and R software, by region, without China. Source: published data by Kit Baum and Posit PBC, own calculations.}
    \label{fig:stata_r_world}
\end{figure}
The data suggest that downloads from China are not fully captured by the Posit-managed mirror, possibly because of peculiarities of the Chinese internet infrastructure. While this is possible for other countries as well, it is not fully detectable. I have excluded China from all calculations, but the remaining computations should be regarded as indicative as best.

I then aggregate countries and regions into "Global North" and "Global South" (Table~\ref{tab:stata_downloads_global_stats_2024_nochina} for Stata, Table~\ref{tab:r_downloads_global_stats_2024_nochina} for R). 
%
%
\input{outputs/stata_downloads_global_stats_select}
\input{outputs/r_downloads_global_stats_select}
%
%
Differencing the two tables  gives the relative importance of Stata versus R, namely that there are relatively more downloads of Stata packages in the Global North than there are of R binaries, suggesting (very tentatively) that Stata usage may be higher in the Global North (Table~\ref{tab:ns_compare})
Reverting back to smaller regions, however, paints the more nuanced picture referenced in the main text (Table~\ref{tab:region_compare}). Tables~\ref{tab:ns_compare} and~\ref{tab:region_compare} are summarized in Figure~\ref{fig:downloads} in the main text.

\input{outputs/compare_ns_stats_select}
\input{outputs/compare_region_stats_select}

### 2025-07-17 outputs/table_access_provision.tex
Should be pretty complete

\begin{table}[!h]
\centering
\caption{\label{tab:access_provision}Access categories and whether data can be shared privately}
\centering
\begin{tabular}[t]{lllrl}
\toprule
Access restrictions & No & Yes & Total & Percent\\
\midrule
No &  & n/a & 50 & \\
\midrule\\
Very Easy to Obtain & 11 & 7 & 18 & (38.89\%)\\
Moderately Easy to Obtain & 3 & 5 & 8 & (62.50\%)\\
Moderately Difficult to Obtain & 16 & 9 & 25 & (36.00\%)\\
Very Difficult to Obtain & 9 & 5 & 14 & (35.71\%)\\
\midrule
\addlinespace
Any restriction & 39 & 26 & 65 & (40.00\%)\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{*} Percentages are calculated as the number of 'Yes' divided by the}\\
\multicolumn{5}{l}{total number of responses. An article can have multiple categories}\\
\multicolumn{5}{l}{of data; the sum of responses is therefore higher than the number}\\
\multicolumn{5}{l}{of articles.}\\
\end{tabular}
\end{table}

>>>>

\begin{table}[!h]
\centering
\caption{\label{tab:access_provision}Access categories and whether data can be shared privately}
\centering
\begin{tabular}[t]{lllrl}
\toprule
Access restrictions & No & Yes & Total & Percent\\
\midrule
No &  & n/a & 50 & \\
\midrule\\
Very Easy to Obtain & 11 & 7 & 18 & (38.89\%)\\
Moderately Easy to Obtain & 3 & 5 & 8 & (62.50\%)\\
Moderately Difficult to Obtain & 16 & 9 & 25 & (36.00\%)\\
Very Difficult to Obtain & 9 & 5 & 14 & (35.71\%)\\
\midrule
\addlinespace
Any restriction & 39 & 26 & 65 & (40.00\%)\\
\bottomrule
\multicolumn{5}{l}{\footnotesize \textsuperscript{*} Percentages are calculated as the number of 'Yes' divided by the}\\
\multicolumn{5}{l}{\footnotesize total number of responses. An article can have multiple categories}\\
\multicolumn{5}{l}{\footnotesize of data; the sum of responses is therefore higher than the number}\\
\multicolumn{5}{l}{\footnotesize of articles.}\\
\end{tabular}
\end{table}

### 2025-07-17 outputs/table_stata-licenses.tex
Should be pretty complete

% latex table generated in R 4.5.1 by xtable 1.8-4 package
% Sat Jun 28 13:39:13 2025
\begin{table}[h]
\centering
\caption{Software licensing internationally} 
\label{tab:licensecost}
\begin{tabular}{lrrrrr}
  \toprule
Country & Average.monthly.income & Stata.license & Laptop & Percent.license & Percent.laptop \\ 
  \midrule
USA & 6,704 & 690 & 849 & 10.3 & 12.7 \\ 
  Greece & 1,883 & 690 & 934.8 & 36.6 & 49.6 \\ 
  Vietnam & 343 & 220 & 706.6 & 64.1 & 206 \\ 
   \midrule \multicolumn{6}{l}{\textit{Notes:} Amounts in USD as of 2025. Source for Stata license prices: Stata website.\newline Sources for laptop prices: HP.com US and German websites, Shopee.vn for Vietnam.} 
 \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.5.1 by xtable 1.8-4 package
% Sat Jun 28 13:39:13 2025
\begin{table}[h]
\centering
\caption{Software licensing internationally} 
\label{tab:licensecost}
\begin{tabular}{lrrrrr}
  \toprule
Country & Average.monthly.income & Stata.license & Laptop & Percent.license & Percent.laptop \\ 
  \midrule
USA & 6,704 & 690 & 849 & 10.3 & 12.7 \\ 
  Greece & 1,883 & 690 & 934.8 & 36.6 & 49.6 \\ 
  Vietnam & 343 & 220 & 706.6 & 64.1 & 206 \\ 
   \midrule 
\multicolumn{6}{l}{\textit{Notes:} Amounts in USD as of 2025. Source for Stata license prices: Stata website.}\\
\multicolumn{6}{l}{ Sources for laptop prices: HP.com US and German websites, Shopee.vn for Vietnam.}\\
 \bottomrule
\end{tabular}
\end{table}
